### 2024-02-20 paper_sisc_first_revision/localpsf.tex
fix "support phi_x" typo

The PSF-based method we propose is loosely based on ``product convolution'' (PC) approximations, which are approximations of an operator by weighted sums of convolution operators with spatially varying weights. PC and PSF methods have a long history dating back several decades. We note the following papers (among many others) in which the convolution kernels are constructed from sampling impulse responses of the operator to scattered point sources:~\cite{Adorf94,AlgerEtAl19,BigotEscandeWeiss19,EscandeWeiss15,EscandeWeiss22,EscandeWeiss12,FishEtAl96,NagyOleary98,ZhuLiFomelEtAl16}. For background on PC and PSF methods, we recommend the following papers: \cite{DenisEtAl15,EscandeWeiss17,GentileCourbinMeylan13}. The proposed PSF-based method improves upon existing PC and PSF methods in the following ways: (1) While PC and PSF approximations are typically based on an assumption of local translation invariance, the method we propose is based on a more general assumption we call ``local mean displacement invariance'' (Section~\ref{sec:local_mean_displacement_invariance} and Figure~\ref{fig:mean_displacement_invariance}), which improves the interpolation of the impulse responses. (2) In our previous work~\cite{AlgerEtAl19}, we chose point sources in an adaptive grid via a sequential procedure; the refinements to the adaptive grid were chosen to maximally reduce the error at each step. However, in that work each point source required a separate operator application, making the previous method expensive when a large number of impulse responses is desired. In this paper, we use a new moment method (Section \ref{sec:intromoments}) which permits computation of many impulse responses (e.g., 50) per operator application. We are inspired by resolution analysis in seismic imaging, in which
$\Aop^T$ is applied to a random noise function, and the width of the support $\phi_x$ is estimated to be the autocorrelation length of the resultant function near $x$~\cite{FichtnerLeeuwen15,TrampertFichtnerRitsema13}. The moment method that we use estimates the support of $\phi_x$ more accurately than random noise probing in resolution analysis, at the cost of the additional constraint that $\Aop$ has a non-negative integral kernel. (3) The PSF-based method we propose never evaluates computed impulse responses outside of their domain of definition. This eliminates ``boundary-artifact'' errors (see \cite[Section 1.1]{AlgerEtAl19}) that plague conventional PC and PSF methods.

>>>>

The PSF-based method we propose is loosely based on ``product convolution'' (PC) approximations, which are approximations of an operator by weighted sums of convolution operators with spatially varying weights. PC and PSF methods have a long history dating back several decades. We note the following papers (among many others) in which the convolution kernels are constructed from sampling impulse responses of the operator to scattered point sources:~\cite{Adorf94,AlgerEtAl19,BigotEscandeWeiss19,EscandeWeiss15,EscandeWeiss22,EscandeWeiss12,FishEtAl96,NagyOleary98,ZhuLiFomelEtAl16}. For background on PC and PSF methods, we recommend the following papers: \cite{DenisEtAl15,EscandeWeiss17,GentileCourbinMeylan13}. The proposed PSF-based method improves upon existing PC and PSF methods in the following ways: (1) While PC and PSF approximations are typically based on an assumption of local translation invariance, the method we propose is based on a more general assumption we call ``local mean displacement invariance'' (Section~\ref{sec:local_mean_displacement_invariance} and Figure~\ref{fig:mean_displacement_invariance}), which improves the interpolation of the impulse responses. (2) In our previous work~\cite{AlgerEtAl19}, we chose point sources in an adaptive grid via a sequential procedure; the refinements to the adaptive grid were chosen to maximally reduce the error at each step. However, in that work each point source required a separate operator application, making the previous method expensive when a large number of impulse responses is desired. In this paper, we use a new moment method (Section \ref{sec:intromoments}) which permits computation of many impulse responses (e.g., 50) per operator application. We are inspired by resolution analysis in seismic imaging, in which
$\Aop^T$ is applied to a random noise function, and the width of the support of $\phi_x$ is estimated to be the autocorrelation length of the resultant function near $x$~\cite{FichtnerLeeuwen15,TrampertFichtnerRitsema13}. The moment method that we use estimates the support of $\phi_x$ more accurately than random noise probing in resolution analysis, at the cost of the additional constraint that $\Aop$ has a non-negative integral kernel. (3) The PSF-based method we propose never evaluates computed impulse responses outside of their domain of definition. This eliminates ``boundary-artifact'' errors (see \cite[Section 1.1]{AlgerEtAl19}) that plague conventional PC and PSF methods.
